Update and evaluation of the ozone dry deposition in the Oslo~CTM3 v1.0

### 2019-07-02 DryDep.tex
Updated plots and started to update tables.

In Section~\ref{sec:model_des}, we will briefly describe the Oslo~CTM3, give a detailed account of the new dry deposition scheme (Section~\ref{subsec:DryDep}) as well as present pre-processing of meteorological input data to compute necessary input to the dry deposition scheme such as begin and duration of greening season (GDAY, GLEN) and photosynthetic photon flux density (PPFD) (Section~\ref{subsec:pre-pro}). In Section~\ref{sec:eval}, we present sensitivity tests with respect to a manifold of parameters in the dry deposition scheme (Section~\ref{subsec:sens}) and validate our results with respect to results from the multi-model intercomparison of \citet{ACP:Hardacre2015} (Section~\ref{subsec:model}) and to surface ozone observations (Section~\ref{subsec:obs}). In Section~\ref{sec:conc}, we will summarize and discuss our results and draw conclusions for further development of the model.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model description}
\label{sec:model_des}
The Oslo~CTM3 is a three dimensional global chemistry transport model (CTM). The key components of the Oslo~CTM3 have been described and evaluated by \citet{GMD:Sovde2012}. A detailed account of the capabilities of the Oslo~CTM3 in simulating anthropogenic aerosol forcing in the past and recent past using the Community Emission Data System (CEDS) historical emission inventory \citep{GMD:Hoesly2018} is given by \citet{GMD:Lund2018}. The Oslo~CTM3 can also be coupled to the Model of Emissions of Gases and Aerosols from Nature (MEGAN v2.10) \citep{ACP:Guenther2006}. A publication focusing on this is planed.

@@

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance is describing the turbulent transport of any substance down to the surface. To derive $R_a^k$, we follow \citet{WASP:Simpson2003,ACP:Simpson2012} and compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with the average wind speed $\overline{u}(z_\mathrm{ref})$ at reference height, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and roughness length $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). We have chosen the model level such that $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. Using the derived $u_*^k$ from Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ can by obtained with \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With these, we get \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$ \citep[e.g.,][]{Garratt1992}. Both integrated stability functions ($\Psi_m$, $\Psi_h$) and corresponding parameters are listed in supplement~S.1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (typically 0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

@@

The phenology of a plant typically describes its life-cycle throughout a year, e.g., at mid latitudes and for deciduous species, it starts with the emergence of leafs in spring and ends in fall. In the mOSaic scheme, phenology is parameterized with respect to the start of greening season (SGS) and its end (EGS). Details about our treatment of these are given in Section~\ref{subsubsec:greening}. In summary, our adaption of the $f_\text{phen}$ parameterization reads as follows:
%
\begin{equation}
  f_\text{phen} =
  \begin{cases}
    \emph{if} \quad \text{GLEN $\ge$ 365} & \quad 1 \quad \emph{(explicitly excluding tropics)} \\
    \emph{if} \quad \text{GDAY = 0}  & \quad 0 \\
    \emph{else}  & \quad 
    \begin{cases}
      \emph{if} \quad \text{GDAY} \le \phi_\text{AS}  & \quad \phi_a \\
      \emph{if} \quad \text{GDAY} \le \phi_\text{AS} + \phi_e  & \quad \phi_b+(\phi_c-\phi_b)\cdot(\text{GDAY}-\phi_\text{AS})/\phi_e\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE} - \phi_f  & \quad \phi_c\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE}  & \quad \phi_d+(\phi_c-\phi_d)\cdot(\text{GLEN}-\phi_\text{AE}-\text{GDAY})/\phi_f\\
      \emph{else} & \quad \phi_d
    \end{cases}
  \end{cases}
  \label{eq:fphen}
\end{equation}
%
Herein, we use the SGS and EGS derived parameters day of greening season (GDAY), the time elapsed starting at the SGS, and the total length of the greening season (GLEN), the time span between EGS and SGS. The parameters $\phi_a$, $\phi_b$, $\phi_c$, and $\phi_d$ define start or end points in the five phases of phenology in the mOSaic scheme, while $\phi_e$, $\phi_f$, $\phi_\text{AS}$, and $\phi_\text{AE}$ control the temporal timing (Fig.~\ref{fig:phenology}). If GLEN is zero we are, e.g., in Arctic regions and there is no vegetation anyway, therefore $f_\text{phen}=0$. Before the start of the growing season ($\text{GDAY}=0$) $f_\text{phen}=0$. Since the mOSaic scheme is tuned to northern hemisphere (NH) mid latitudes, this phenology does not apply to the tropics. We therefore decided to set $f_\text{phen}=1$ if GLEN is greater or equal to 365 which is the case in the tropics.
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig01}
  \caption{Sketch of the five different phases in plant phenology $f_\text{phen}$ in accordance to Eq.~(\ref{eq:fphen}).}
  \label{fig:phenology}
\end{figure}

@@

In this way, vegetation affects the conductance also by being there, not only by uptake through the stomata. The in-canopy resistance $R_\text{inc}$ \citep{AE:Erisman1994} is then modified with respect to each (vegetated) land surface type in $k$
\begin{equation}
  R_\text{inc} = b \cdot \text{SAI}_k \cdot \frac{h_k(\text{lat})}{u_*},
\end{equation}
where $h_k(\text{lat})$ is the latitude dependent vegetation height (see explanation at the end of this section) and $b = 14\,\unit{m^{-1}}$ is an empirical constant. The canopy resistance described in \citet{ACP:Simpson2012} does not take temperature and snow into account and is zero for non-vegetated surfaces, but we will adopt the correction previously used in the Oslo~CTM3 Wesely scheme.\\
As initially mentioned, the necessary depth of snow to cover a certain type of vegetation differs. Therefore, we calculate a snow cover fraction $f_\text{snow}$ using the snow depth $S_D$, which is available in units of meter of water equivalent from the meteorological input data, scaled to $10\,\unit{\%}$ of the vegetation height.
$R_\text{gs}^{\chem{O_3},k}$ is tabulated and we correct for temperature by $F_T$ and for snow cover fraction:
\begin{equation}
  \frac{1}{R_\text{gs}^{\chem{O_3},k}} = \frac{1-f_\text{snow}}{\hat{R}_\text{gs}^{\chem{O_3},k}} + \frac{f_\text{snow}}{R_\text{snow}^\chem{O_3}}.
\end{equation}

The bulk canopy conductance is then defined as:
\begin{equation}
  G_c^k = \text{LAI} \cdot g^k_\text{sto, m} + G^k_\text{ns}, 
\end{equation}
wherein $\text{LAI}$ is the one-sided leaf area index taken from ISLSCP2 FASIR (zero for non-vegetated surfaces), $g_\text{sto}$ the leaf-level stomatal conductance, and $G_\text{ns}$ the bulk non-stomatal conductance.\\

@@

\begin{table*}[t]
  \caption{Summary of specifications of all simulations discussed in this section. For simplicity, only the tested parameters are listed. An x denotes that the model was run exactly in the configuration as has been described in Section~\ref{sec:model_des}.}
  \begin{tabular}{lccccccccc}
    \tophline
    \multirow{2}{*}{Simulation} & Wesely scheme & \multicolumn{3}{c}{mOSaic scheme} & \multicolumn{2}{c}{Greening season} & $v^\chem{O_3}_\text{ice/snow}$ & Emissions\\
    & & $f_\text{phen}$ & $f_\text{light}$ & $f_\text{SW}$ & SMOKE-BEIS & $5\,\unit{^\circ C}$-days & (\unit{m\,s^{-1}}) & (year)\\
    \middlehline
    Wesely\_type      & x & \multicolumn{3}{c}{n/a}  & x & n/a   & 1/2000  & 2014 \\
    EMEP\_full        &   & incl. TR & x & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_offLight    &   & incl. TR & 1 & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_offPhen     &   & 1        & x & SWLV1     & x &       & 1/2000  & 2014 \\
    EMEP\_SWVL4       &   & incl. TR & x & SWLV4     & x &       & 1/2000  & 2014 \\
    EMEP\_ppgs        &   & incl. TR & x & SWLV1     &   & NH    & 1/2000  & 2014 \\
    EMEP\_ppgs\_2005  &   & incl. TR & x & SWLV1     &   & NH    & 1/2000  & 2005 \\
    EMEP\_ppgssh      &   & excl. TR & x & SWLV1     &   & NH+SH & 1/2000  & 2014 \\
    EMEP\_ppgssh\_ice &   & excl. TR & x & SWLV1     &   & NH+SH & 1/10000 & 2014 \\
    \bottomhline
  \end{tabular}
  \label{tab:simsum}
  %\belowtable{} % Table Footnotes
\end{table*}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig04}
  \caption{Relative difference between the sensitivity simulation \emph{EMEP\_ppgsssh} and the \emph{Wesely\_type} in (a) total surface ozone; (b) average ozone dry deposition velocity; (c) total amount of ozone removed from the atmosphere by dry deposition.}
  \label{fig:diff_maps}
\end{figure}
%
In Fig.~\ref{fig:diff_maps}, we show the average relative difference between \emph{EMEP\_ppgsssh} and \emph{Wesely\_type} on global maps by means of surface ozone burden, dry deposition velocity and total ozone dry deposition. Surface ozone increases globally except for regions covered by tropical forest. Especially in desert regions in Africa and Asia, surface ozone increases by up to $100\,\unit{\%}$. Consistently, dry deposition velocities decrease globally by the same order of magnitude in these regions, while they increase over tropical forest. With respect to total dry deposition, the picture is a bit less clear. We find a decrease of total dry deposition of ozone in desert regions and ocean covered areas and an increase in regions covered by tropical forest, while at mid and high latitudes in both hemispheres only small changes are visible. A possible explanation to this divergence especially in desert regions is the difference between the prescribed dry deposition velocities in the Wesely scheme in comparison to those used in the mOSaic scheme. We cover this in more detail in the following section.

>>>>

In Section~\ref{sec:model_des}, we will briefly describe the Oslo~CTM3, give a detailed account of the new dry deposition scheme (Section~\ref{subsec:DryDep}) as well as present pre-processing of meteorological input data to compute necessary input to the dry deposition scheme such as begin and duration of greening season (GDAY, GLEN) and photosynthetic photon flux density (PPFD) (Section~\ref{subsec:pre-pro}). In Section~\ref{sec:eval}, we present sensitivity tests with respect to a manifold of parameters in the dry deposition scheme (Section~\ref{subsec:sens}) and validate our results with respect to results from the multi-model intercomparison of \citet{ACP:Hardacre2015} (Section~\ref{subsec:model}) and to surface ozone observations (Section~\ref{subsec:obs}). In Section~\ref{sec:conc}, we will summarize and discuss our results and draw conclusions for further development of the model.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Model description}
\label{sec:model_des}
The Oslo~CTM3 is an offline, three dimensional, global chemistry transport model (CTM). The key components of the Oslo~CTM3 have been described and evaluated by \citet{GMD:Sovde2012}. A detailed account of the capabilities of the Oslo~CTM3 in simulating anthropogenic aerosol forcing in the past and recent past using the Community Emission Data System (CEDS) historical emission inventory \citep{GMD:Hoesly2018} is given by \citet{GMD:Lund2018}. The Oslo~CTM3 can also be coupled to the Model of Emissions of Gases and Aerosols from Nature (MEGAN v2.10) \citep{ACP:Guenther2006}. A publication focusing on this is planed.

@@

\subsubsection{Aerodynamic resistance}
\label{subsubsec:Ra}
In general, the aerodynamic resistance is describing the turbulent transport of any substance down to the surface. To derive $R_a^k$, we follow \citet{WASP:Simpson2003,ACP:Simpson2012} and compute a local friction velocity at reference height $z_\mathrm{ref}$ \citep[Eq.~(52),][]{ACP:Simpson2012}
\begin{equation}
  u_*^k = \frac{\overline{u}(z_\mathrm{ref})\cdot\kappa}{\ln{(\frac{z_\mathrm{ref}-d_k}{z_0^k})}-\Psi_m(\frac{z_\mathrm{ref}-d_k}{L})+\Psi_m(\frac{z_0^k}{L})},
  \label{eq:local_fric_vel}
\end{equation}
with the average wind speed $\overline{u}(z_\mathrm{ref})$ at reference height, the K\'{a}rm\'{a}n constant $\kappa = 0.40$, the integrated stability equation for momentum $\Psi_m$ \citep[e.g.,][]{Garratt1992}, a grid average Obukhov length $L$, deplacement height $d_k$, and roughness length $z_0^k$ ($d_k=0.78\cdot h_k(\mathrm{lat})$, $z_0^k=0.07\cdot h_k(\mathrm{lat})$ for forests, $d_k=0.7\cdot h_k(\mathrm{lat})$, $z_0^k=0.1\cdot h_k(\mathrm{lat})$ for vegetation other than forests). We have chosen the model level such that $\overline{z}_\mathrm{ref}\approx 45\,\unit{m}$. Using the derived $u_*^k$ from Eq.~(\ref{eq:local_fric_vel}), a local Obukhov length $L_k$ can by obtained with \citep[Eq.~(8),][]{ACP:Simpson2012}:
\begin{equation}
  L_k = - \frac{\rho c_p T_\mathrm{2m} u_*^k}{\kappa g H}.
\end{equation}
Herein, $H$ is the sensible heat flux, $g$ is the standard gravitational acceleration, $c_p$ the specific heat capacity, and $T_{2m}$ the $2\,\unit{m}$ temperature. With these, we can compute the aerodynamical resistance for each land surface type \citep[Eq.~(8.8),][]{WASP:Simpson2003}
\begin{equation}
  R_a^k = \frac{1}{\kappa u_*^k}\left[{\ln{\left(\frac{z_\mathrm{ref}-d_k}{z_0^k}\right)}-\Psi_h\left(\frac{z_\mathrm{ref}-d_k}{L_k}\right)+\Psi_h\left(\frac{z_0^k}{L_k}\right)}\right],
\end{equation}
with the integrated stability equation for heat $\Psi_h$ \citep[e.g.,][]{Garratt1992}. Both integrated stability functions ($\Psi_m$, $\Psi_h$) and corresponding parameters are listed in supplement~S.1.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Quasi-laminar layer resistance}
\label{subsubsec:Rb}
The quasi-laminar layer resistance $R_b^{i,k}$ is species specific and differs over land and ocean surfaces.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Over land, we use \citep[Eq.~(53),][]{ACP:Simpson2012}
\begin{equation}
  R_b^{i,k} = \frac{2}{\kappa u_*} \cdot \left(\frac{\text{Sc}_i}{\text{Pr}}\right)^{\frac{2}{3}},
  \label{eq:Rb}
\end{equation}
wherein $\text{Pr}$ is the Prandtl number (typically 0.72 for air and other gases) and $\text{Sc}_i$ is the Schmidt number for a gas $i$. Eq.~(\ref{eq:Rb}) differs from a similar formulation in \citet{ACP:Seinfeld2006} by a factor of roughly $1.25$. From $\text{Sc}_i = \nu/D_i$, with the kinematic viscosity of air $\nu$, we derive a Schmidt number in water equivalent:
\begin{equation}
  \text{Sc}_i = \frac{D_\chem{H_2O}}{D_i} \cdot \text{Sc}_\chem{H_2O},
\end{equation}
with the molecular diffusivity for any gas $D_i$, the Schmidt number of water ($\text{Sc}_\chem{H_2O}=0.6$) and its molecular diffusivity ($D_\chem{H_2O}=0.21\cdot10^{-4}\,\unit{m^2\,s^{-1}}$). The used ratios $D_\chem{H_2O}/D_i$ are taken from \citet[][Table S18]{ACP:Simpson2012}.\\

@@

The phenology of a plant typically describes its life-cycle throughout a year, e.g., at mid latitudes and for deciduous species, it starts with the emergence of leafs in spring and ends in fall. In the mOSaic scheme, phenology is parameterized with respect to the start of greening season (SGS) and its end (EGS). Details about our treatment of these are given in Section~\ref{subsubsec:greening}. In summary, our adaption of the $f_\text{phen}$ parameterization reads as follows:
%
\begin{equation}
  f_\text{phen} =
  \begin{cases}
    \emph{if} \quad \text{GLEN $\ge$ 365} & \quad 1 \quad \emph{(explicitly excluding tropics)} \\
    \emph{if} \quad \text{GDAY = 0}  & \quad 0 \\
    \emph{else}  & \quad 
    \begin{cases}
      \emph{if} \quad \text{GDAY} \le \phi_\text{AS}  & \quad \phi_a \\
      \emph{if} \quad \text{GDAY} \le \phi_\text{AS} + \phi_e  & \quad \phi_b+(\phi_c-\phi_b)\cdot(\text{GDAY}-\phi_\text{AS})/\phi_e\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE} - \phi_f  & \quad \phi_c\\
      \emph{if} \quad \text{GDAY} \le \text{GLEN} - \phi_\text{AE}  & \quad \phi_d+(\phi_c-\phi_d)\cdot(\text{GLEN}-\phi_\text{AE}-\text{GDAY})/\phi_f\\
      \emph{else} & \quad \phi_d
    \end{cases}
  \end{cases}
  \label{eq:fphen}
\end{equation}
%
Herein, we use the SGS and EGS derived parameters day of greening season (GDAY), the time elapsed starting at the SGS, and the total length of the greening season (GLEN), the time span between EGS and SGS. The parameters $\phi_a$, $\phi_b$, $\phi_c$, and $\phi_d$ define start or end points in the five phases of phenology in the mOSaic scheme, while $\phi_e$, $\phi_f$, $\phi_\text{AS}$, and $\phi_\text{AE}$ control the temporal timing (Fig.~\ref{fig:phenology}). If GLEN is zero we are, e.g., in Arctic regions and there is no vegetation anyway, therefore $f_\text{phen}=0$. Before the start of the greening season ($\text{GDAY}=0$) $f_\text{phen}=0$. Since this phenology is tuned to northern hemisphere (NH) mid latitudes, it does not apply to the tropics. We therefore decided to set $f_\text{phen}=1$ if GLEN is greater or equal to 365 which is the case in the tropics.
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig01}
  \caption{Sketch of the five different phases in plant phenology $f_\text{phen}$ in accordance to Eq.~(\ref{eq:fphen}).}
  \label{fig:phenology}
\end{figure}

@@

In this way, vegetation affects the conductance also by being there, not only by uptake through the stomata. The in-canopy resistance $R_\text{inc}$ \citep{AE:Erisman1994} is then modified with respect to each (vegetated) land surface type in $k$
\begin{equation}
  R_\text{inc} = b \cdot \text{SAI}_k \cdot \frac{h_k(\text{lat})}{u_*},
\end{equation}
where $h_k(\text{lat})$ is the latitude dependent vegetation height (see explanation at the end of this section) and $b = 14\,\unit{m^{-1}}$ is an empirical constant. The canopy resistance described in \citet{ACP:Simpson2012} does not take temperature and snow into account and is zero for non-vegetated surfaces, but we will adopt the correction previously used in the Oslo~CTM3 Wesely scheme.\\
As initially mentioned, the necessary depth of snow to cover a certain type of vegetation differs. Therefore, we calculate a snow cover fraction $f_\text{snow}$ using the snow depth $S_D$, which is available in units of meter of water equivalent from the meteorological input data, scaled to $10\,\unit{\%}$ of the vegetation height.
$R_\text{gs}^{\chem{O_3},k}$ is tabulated. We correct for temperature by $F_T$ and for snow cover fraction:
\begin{equation}
  \frac{1}{R_\text{gs}^{\chem{O_3},k}} = \frac{1-f_\text{snow}^k}{\hat{R}_\text{gs}^{\chem{O_3},k}} + \frac{f_\text{snow}^k}{R_\text{snow}^{\chem{O_3},k}}.
\end{equation}

The bulk canopy conductance is then defined as:
\begin{equation}
  G_c^k = \text{LAI} \cdot g^k_\text{sto, m} + G^k_\text{ns}, 
\end{equation}
wherein $\text{LAI}$ is the one-sided leaf area index taken from ISLSCP2 FASIR, $g_\text{sto}$ the leaf-level stomatal conductance, and $G_\text{ns}$ the bulk non-stomatal conductance.\\

@@

\begin{table*}[t]
  \caption{Summary of specifications of all simulations discussed in this section. For simplicity, only the tested parameters are listed. An x denotes that the model was run exactly in the configuration as has been described in Section~\ref{sec:model_des}.}
  \begin{tabular}{lccccccccc}
    \tophline
    \multirow{2}{*}{Simulation} & \multicolumn{3}{c}{mOSaic scheme} & \multicolumn{2}{c}{Greening season} & $R^\chem{O_3}$ & Emissions\\
    & $f_\text{phen}$ & $f_\text{light}$ & $f_\text{SW}$ & SMOKE-BEIS & $5\,\unit{^\circ C}$-days & & (year)\\
    \middlehline
    Wesely\_type      &  \multicolumn{3}{c}{n/a}   & x & n/a& \citet{AE:Wesely1989, JGR:Hough1991}  & 2005 \\
    mOSaic            &   x & x & x                &   &  x & x  & 2005 \\
    mOSaic\_offLight  &   x & 1 & x                &   &  x & x  & 2005 \\
    mOSaic\_offPhen   &   1 & x & x                &   &  x & x  & 2005 \\
    mOSaic\_SWVL1     &   x & x & SWLV1            &   &  x & x  & 2005 \\
    mOSaic\_ice       &   x & x & x                &   &  x & x; \citet{ACP:Helmig2007}$^\dagger$ & 2005 \\
    mOSaic\_desert    &   x & x & x                &   &  x & x; \citet{AE:Gusten1995}$^*$  & 2005 \\
    mOSaic\_emis2014  &   x & x & x                &   &  x & x  & 2014 \\
    mOSaic\_hough     &   x & x & x                &   &  x & \citet{AE:Wesely1989, JGR:Hough1991}$^\star$  & 2005 \\
    \bottomhline
  \end{tabular}
  \label{tab:simsum}
  \belowtable{$^\dagger\,R^\chem{O_3}_\text{ice/snow}=10000\,\unit{s\,m^{-1}}$; $^*\,R^\chem{O_3}_\text{desert}=800\,\unit{s\,m^{-1}}$; $^\star\,$Supplement~S.7} % Table Footnotes
\end{table*}
%
\begin{figure}[t]
  \includegraphics[width=8.3cm]{fig04}
  \caption{Relative difference between the sensitivity simulation \emph{EMEP\_ppgsssh} and the \emph{Wesely\_type} in (a) total surface ozone; (b) average ozone dry deposition velocity; (c) total amount of ozone removed from the atmosphere by dry deposition.}
  \label{fig:diff_maps}
\end{figure}
%
In Fig.~\ref{fig:diff_maps}, we show the average relative difference between \emph{EMEP\_ppgsssh} and \emph{Wesely\_type} on global maps by means of surface ozone burden, dry deposition velocity and total ozone dry deposition. Surface ozone increases globally except for regions covered by tropical forest. Especially in desert regions in Africa and Asia, surface ozone increases by up to $100\,\unit{\%}$. Consistently, dry deposition velocities decrease globally by the same order of magnitude in these regions, while they increase over tropical forest. With respect to total dry deposition, the picture is a bit less clear. We find a decrease of total dry deposition of ozone in desert regions and ocean covered areas and an increase in regions covered by tropical forest, while at mid and high latitudes in both hemispheres only small changes are visible. A possible explanation to this divergence especially in desert regions is the difference between the prescribed dry deposition velocities in the Wesely scheme in comparison to those used in the mOSaic scheme. We cover this in more detail in the following section.

### 2019-07-02 DryDep_supplement.tex
Updated plots and started to update tables.

\begin{document}
\clearpage
\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplement}
\subsection*{S.1 Aerodynamical resistance}
\begin{equation}
  \Psi_m(\zeta) =
  \begin{cases}
   \log(\frac{1+x^2}{2}\cdot(\frac{1+x}{2})^2) - 2\cdot \arctan(x+\frac{\pi}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psim}
\end{equation}
\begin{equation}
  \Psi_h(\zeta) =
  \begin{cases}
   2\cdot\log(\frac{1+x^2}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psim}
\end{equation}
$x = (1-\gamma\cdot\zeta)^\frac{1}{4}$, $\beta = 4.7$, $\gamma = 15$ (from Cansas experiment).
%\begin{table}[!htbp]
%  \caption{Molecular diffusivity for a gas $i$ given as ration $D_\chem{H_2O}/D_i$, reactivity $f^i_0$, and effective Henry's Law constant $H^i_*$.}
%  \begin{tabular}{lcrr@{$\cdot$}l}
%    \tophline
%    & $D_\chem{H_2O}/D_i$ & $f^i_0$ & \multicolumn{2}{l}{$H^i_*$}\\
%    & & & \multicolumn{2}{l}{(\unit{M\,atm^{-1}})}\\
%    \middlehline
%    \chem{O_3}     & 1.6 & 1.0 & 1 & $10^{-2}$\\
%    \chem{SO_2}    & 1.9 & 0.0 & 1 & $10^5$\\
%    \chem{NO_2}    & 1.6 & 0.1 & 1 & $10^{-2}$\\
%    \chem{H_2O_2}  & 1.4 & 1.0 & 1 & $10^5$\\
%    \chem{HCHO}    & 1.3 & 0.0 & 6 & $10^3$\\
%    \chem{NO}      & 1.3 & 0.0 & 2 & $10^{-3}$\\
%    \chem{CH_3CHO} & 1.6 & 15.0 & \multicolumn{2}{l}{$0$}\\
%    \bottomhline
%  \end{tabular}
  %\belowtable{} % Table Footnotes
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{S.2 Dynamic viscosity of air and quasi-laminar resistance}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity.pdf}
  \caption{Sutherland's law and divergence linear fits with one or two degrees of freedom. The fit $\mu(T) = m\cdot T$ is implemented in the Oslo~CTM3. Despite its strong divergence at lower and higher temperatures, the impact of this choice on the results is negligible.}
\end{figure}
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity_zo_Rb.pdf}
  \caption{Comparison of resulting $z_o$ and $R_b$ for $\mu(T) = m\cdot T$  (left panel) and Sutherland's law (right panel). The example displays the distributions for \chem{H_2O} after one day of model integration for both, rough and calm sea case.}
\end{figure}

@@

\end{document}

>>>>

\begin{document}
\clearpage
\setcounter{page}{1}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Supplement}
\subsection*{S.1 Aerodynamical resistance}
\begin{equation}
  \Psi_m(\zeta) =
  \begin{cases}
   \log(\frac{1+x^2}{2}\cdot(\frac{1+x}{2})^2) - 2\cdot \arctan(x+\frac{\pi}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psim}
\end{equation}
\begin{equation}
  \Psi_h(\zeta) =
  \begin{cases}
   2\cdot\log(\frac{1+x^2}{2}) & \quad \emph{if} \quad -2 < \zeta < 0,\\
   - \beta \cdot \zeta & \quad \emph{if} \quad \zeta \ge 0.
  \end{cases}
  \label{eq:psih}
\end{equation}
$x = (1-\gamma\cdot\zeta)^\frac{1}{4}$, $\beta = 4.7$, $\gamma = 15$ (from Kansas experiment).
%\begin{table}[!htbp]
%  \caption{Molecular diffusivity for a gas $i$ given as ration $D_\chem{H_2O}/D_i$, reactivity $f^i_0$, and effective Henry's Law constant $H^i_*$.}
%  \begin{tabular}{lcrr@{$\cdot$}l}
%    \tophline
%    & $D_\chem{H_2O}/D_i$ & $f^i_0$ & \multicolumn{2}{l}{$H^i_*$}\\
%    & & & \multicolumn{2}{l}{(\unit{M\,atm^{-1}})}\\
%    \middlehline
%    \chem{O_3}     & 1.6 & 1.0 & 1 & $10^{-2}$\\
%    \chem{SO_2}    & 1.9 & 0.0 & 1 & $10^5$\\
%    \chem{NO_2}    & 1.6 & 0.1 & 1 & $10^{-2}$\\
%    \chem{H_2O_2}  & 1.4 & 1.0 & 1 & $10^5$\\
%    \chem{HCHO}    & 1.3 & 0.0 & 6 & $10^3$\\
%    \chem{NO}      & 1.3 & 0.0 & 2 & $10^{-3}$\\
%    \chem{CH_3CHO} & 1.6 & 15.0 & \multicolumn{2}{l}{$0$}\\
%    \bottomhline
%  \end{tabular}
  %\belowtable{} % Table Footnotes
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{S.2 Dynamic viscosity of air and quasi-laminar resistance}
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity.pdf}
  \caption{Sutherland's law and divergence linear fits with one or two degrees of freedom. The fit $\mu(T) = m\cdot T$ is implemented in the Oslo~CTM3. Despite its strong divergence at lower and higher temperatures, the impact of this choice on the results is negligible.}
\end{figure}
%
\begin{figure}[!htbp]
  \centering
  \includegraphics[height=0.4\textheight]{pictures/dynamic_viscosity_zo_Rb.pdf}
  \caption{Comparison of resulting $z_o$ and $R_b$ for $\mu(T) = m\cdot T$  (left panel) and Sutherland's law (right panel). The example displays the distributions for \chem{H_2O} after one day of model integration for both, rough and calm sea case.}
\end{figure}

@@

\subsection*{S.7 Wesely-Hough $R^\chem{O_3}$}
\begin{table*}[!htbp]
  \caption{Surface resistance of ozone: $^*$ CF -- temperate/boreal coniferous; DF -- temperate/boreal deciduous; NF -- Mediterranean needleleaf; BF -- Mediterranean broadleaf; TC -- temperate crop; MC -- Mediterranean crop; RC -- root crop; SNL -- moorland; GR -- grass; MS -- Mediterranean shrub; WE -- wetlands; TU -- tundra; DE -- desert; W -- water; ICE -- ice.}
  \begin{tabular}{lc}
    \tophline
    Code$^*$ & $R_\chem{O_3}$\\
         & (\unit{s\,m^{-1}})\\
    \middlehline
    CF &  1000\\
    DF &  1000 \\
    NF &  1000 \\
    BF &  1000 \\
    TC &  200 \\
    SNL & 400 \\
    GR  & 1000 \\
    MS  & 1000 \\
    WE  & 400 \\
    TU  & 385 \\
    DE  & 385 \\
    W   & 1430 \\
    U   & 400 \\
    ICE & 1430\\
    \bottomhline
 \end{tabular}
  %\belowtable{}
\end{table*}
\end{document}
